Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-24 paper.tex
almost finished experiment description
tackling PPHW comments

Fuel cycle simulations, as with any simulation process, do not produce results
without errors.  Those errors have different sources: data uncertainties (from
%% I'm not a fan of the use of the word ``errors'' here.  We should be careful
%% since (in English) this can meam ``mistakes''.  Uncertainty is a better
%% word, and then we'll have to distinguish between input uncertainties and
%% output uncertainties.
the simulator's reliance on previously estimated/measured data), modeling
uncertainties (from simplifications made by the simulator) and the
``operational'' uncertainty (from the expected behavior of the facilities
being simulated).
%% is this operational uncertainty really just a different kind of data?

Simulation errors could be important in the context of treaty verification. 
Some scenarios require estimating historical fissile
material production based on records of facility operation and material
transfer.  If the measurements of facility operation and material transfer are
subject to uncertainty, the total production quantities will then also be
uncertain.  Any uncertainty in fissile production quantities poses a material
accounting challenge, possibly
creating an opportunity for undetected diversion.  This study seeks
to understand which measures of facility operation have the most impact on the
uncertainty of fissile material production across a complete fuel cycle.
To accomplish this, a Total Monte Carlo methodology will be applied to the Cyclus
fuel cycle simulator \cite{cyclus} to estimate the effect of individual facility uncertainties on the output metrics.
%% should there be a reference for Total Monte Carlo?

% I don't think Total Monte Carlo should be in quotes
\section{The Experiment}

@@

\begin{table}[htb]
\centering
  \caption{Summary of facility modifications according to their Cyclus archetype package.}
\begin{tabular}{cll}
\toprule

Package   & Facility   & Parameters                \\
\midrule
Cycamore & Separation & Separation efficiency     \\ %% add hline in 2nd two columns
         & Storage    & Residence Time            \\
\midrule
CyCLASS  & Reactor    & Cycle Length              \\
         &            & Power                     \\
         &            & Fuel Enrichment (PWR-UOX) \\

@@

\subsection{The Fuel Cycle Scenario}
For demonstration purposes, a simple commercial fuel cycle transition is used,
inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
Pictured in Figure \ref{fig:cycle}, this is a
transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the nuclear generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Simplified representation of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}
%% Update this to match the one in the CVT poster?

@@

Both fuel reprocessing and fabrication are done at a constant rate (constrained
by the feed material availability).  The enrichment of the \gls{UOX} is processed
%% is it really a constant rate then?  Maybe we need a better word to describe this
on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
%% You can't pluralize ``storage'' in English - it's considered uncountable
between all facilities with constant processing rates.

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a given target
burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
enrichment is not applied directly to the effective enrichment. It is instead applied to the
burnup, which leads to a fuel enrichment uncertainty close to
$10\%$.
%% Did you have to experiment to find the burnup uncertainty that results in a 10% enrichment uncertainty?

@@

Because the main interests of nuclear archaeology involve highly enriched uranium production and
fissile inventories, this study mainly focuses on the uncertainties of
the total quantity of natural uranium used and the total unused fissile
inventory (unused reprocessed plutonium).
%% unused implies it's never used, but I don't think that's right.  You just mean the amount
%% that is being stored in a separated state any point in time, right?
Generated power is also briefly investigated to ensure the overall
uncertainty is not contaminated with a missed fuel loading, which could
be interesting but is not the focus of this work.
%% what do you mean by contaminated???  This probably deserves more explanation

@@

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understood as an averaging effect.  As the uncertainty are defined once
per deployed facility, each reactor will have a different cycle
length value, so a different number of batches loaded per year.  With the increase
of deployed reactors, the number of batches of \gls{LWR} fuel loaded converges
to the references one, reducing its impact on the uncertainty on the total
uranium consumption.
%% Why does the relative uncertainty due to cyle time not approach 0?

@@

Regarding the uncertainty, disregarding the artefact of a very low mean inventory
observed at the onset of fissile material production, the relative uncertainty
starts at about $5\%$, and grows until year
125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
%% I don't see what you mean by decrease up to 10%?
it would have reached an equilibrium between $5$ and $10\%$ with longer
simulations...
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length.  As with the uranium needs, lower cycle length
implies more fuel loads.  Never the less, around year 65 (see Figure
%% Aren't you varying the cycle length equally to be smaller and larger, so why
%% focus on ``lower cycle lengths''?
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
small enough to start limiting producton of fissile material.
The uncertainty weight is then slowly transferred from
the cycle length to the fuel cooling time.

>>>>

Fuel cycle simulations, as with any simulation process, do not produce results
without uncertainties.  Those uncertainties have different sources: data uncertainties (from
the simulator's reliance on previously estimated/measured data), modeling
uncertainties (from simplifications made by the simulator). This work we will be
focused a part of the data uncertainty related to the expected behavior of the
facilities being simulated.

Simulation errors could be important in the context of treaty verification.
Some scenarios require estimating historical fissile material production based
on records of facility operation and material transfer.  If the measurements of
facility operation and material transfer are subject to uncertainty, the total
production quantities will then also be uncertain.  Any uncertainty in fissile
production quantities poses a material accounting challenge, possibly creating
an opportunity for undetected diversion.

This study seeks to understand which measures of facility operation have the
most impact on the uncertainty of fissile material production across a complete
fuel cycle.  Uncertainty propagation using a Monte Carlo method will be applied
to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect of
individual facility uncertainties on the output metrics. The same simulation
will be simulated $N$ times, for each simulation parameters affected with an
uncertainty will be randomly determined, the distribution of each output metrics
over the N iterations of the simulation, will be used to estimate their
respective uncertainty.

\section{The Experiment}

@@

\begin{table}[htb]
\centering
  \caption{Summary of facility modifications according to their Cyclus archetype package.}
\begin{tabular}{cl|l}
\toprule

Package   & Facility   & Parameters                \\
\midrule
Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
         & Storage    & Residence Time            \\
\midrule
CyCLASS  & Reactor    & Cycle Length              \\
         &            & Power                     \\
         &            & Fuel Enrichment (PWR-UOX) \\

@@

\subsection{The Fuel Cycle Scenario}
For demonstration purposes, a simple commercial fuel cycle transition is used,
inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
Pictured in Figure \ref{fig:cycle}, this is a
transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the nuclear generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Simplified representation of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

@@

Both fuel reprocessing and fabrication rate are both limited by the facilities
throughput and the ressource available.  The enrichment of the \gls{UOX} is processed
on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
between all facilities with constant processing rates.

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a given target
burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
enrichment is not applied directly to the effective enrichment. It is instead applied to the
burnup, which appears to lead to a fuel enrichment uncertainty close to
$10\%$.

@@

Because the main interests of nuclear archaeology involve highly enriched uranium production and
fissile inventories, this study mainly focuses on the uncertainties of
the total quantity of natural uranium used and the total unused fissile
inventory (separated plutonium).
Generated power is also briefly investigated to ensure the overall
uncertainty is not contaminated with a missed fuel loading, which could
be interesting but is not the focus of this work. It is assumed that no reactor
are unexpectedly shutdown because of fuel shortage, as such events should be well
documented...

@@

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understood as an averaging effect.  As the uncertainty are defined once
per deployed facility, each reactor will have a different cycle
length value, so a different number of batches loaded per year.  With the increase
of deployed reactors, the number of batches of \gls{LWR} fuel loaded converges
to the references one, reducing its impact on the uncertainty on the total
uranium consumption. This uncertainty contribution to the overall uncertainty
decrease is proportional to the number of \gls{LWR} reactors and stops with the
decommission of the last one.

@@

Regarding the uncertainty, disregarding the artefact of a very low mean inventory
observed at the onset of fissile material production, the relative uncertainty
starts at about $5\%$, and grows until year
125 to decrease to $10\%$ at the end of the simulation time (180y), it seems
%% I don't see what you mean by decrease up to 10%?
it would have reached an equilibrium between $5$ and $10\%$ with longer
simulations...
Between year 40 and 70, the main contributor to the fissile inventory
uncertainty is the cycle length.  As with the uranium needs, different cycle length
implies different number of fuel loads, so different amount of resources used.  Never the less, around year 65 (see Figure
\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
small enough to start limiting production of fissile material.
The uncertainty weight is then slowly transferred from
the cycle length to the fuel cooling time.
